
---
title: "Sleep Health and Lifestyle Dataset"
subtitle: "Analiza jakości snu na podstawie stylu życia"
author: "StowarzyszenieOvi <br> viol68, Tamirami, rvai00"
institute: "Nicolaus Copernicus University in Toruń"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(datasets)
library(ggplot2)
library(kableExtra)
library(corrplot)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r, include=FALSE}
getwd()
```

```{r, include=FALSE}
# Specify the path to your CSV file
file_path <- "Sleep_dataset.csv"

# Load data from the CSV file into a data frame
Sleep_dataset <- read.csv(file_path)

```

```{r, echo=FALSE}
style_xaringan(
  title_slide_background_image = "img/background_img2.webp"
)
```

class: inverse, center, middle
# **Cel Badawczy**
Nasza praca na celu analizę zbioru danych dotyczącego snu i stylu życia, ze szczególnym uwzględnieniem zawodów respondentów. Dążymy do zidentyfikowania potencjalnych zależności i wzorców, skupiając się na różnicach wynikających z różnych profesji. Zależy nam na zrozumieniu, czy istnieją konkretne zawody, które bardziej niż inne doświadczają trudności związanych ze snem.

---
class: inverse, center, middle
# O bazie danych
Zestaw danych dotyczący snu i stylu życia zawiera 400 wierszy i 13 kolumn, obejmujących szeroki zakres zmiennych związanych ze snem i codziennymi nawykami. Zmienne, na podstawie których została wykonana analiza to:

```{r wyświetlenie_zmiennych, echo=FALSE}
names(Sleep_dataset)
```

---
#Dane demograficzne

```{r rozkład_płci, echo = FALSE}
ggplot(Sleep_dataset, aes(x = Gender, fill = Gender)) +
  geom_bar() +
  geom_text(aes(label = after_stat(count)), stat = "count", vjust = 1.5, colour = "white") +
  scale_fill_manual(values = c("#9999CC", "#66CC99")) +
theme(panel.background = element_rect(fill = "#FCE4EC"))
```

```{r rozkład_wieku}
ggplot(Sleep_dataset, aes(x = Age, fill = Age)) +
  geom_histogram(binwidth = 5, color = "#871F78", position = "identity") +
  scale_fill_viridis_c() +
  labs(title = "Rozkład Wieku", x = "Wiek", y = "Liczba osób") +
  theme(panel.background = element_rect(fill = "#FCE4EC"))
```


---
#Wykonywane zawody przez badanych
```{r, echo=FALSE}
ggplot(Sleep_dataset, aes(x = Occupation, fill=Occupation)) +
  geom_bar() +
  labs(y = "Count") +
  theme(axis.text.x=element_text(size=10, angle=45,hjust=0.95))
```

---
```{r matrix}
numeric_Sleep_dataset <- df[sapply(df, is.numeric)]

# Calculate the correlation matrix
correlation_matrix <- cor(numeric_Sleep_dataset)

# Plot the heatmap
corrplot(correlation_matrix, method="color", addCoef.col="black", tl.col="black", tl.srt=45)
```






---
```{r, echo=FALSE}

library(dplyr)
library(ggplot2)

# Calculate average stress level for each occupation
average_stress_by_occupation <- Sleep_dataset %>%
  group_by(Occupation) %>%
  summarize(Average_Stress = mean(Stress.Level, na.rm = TRUE))

# Create a histogram
ggplot(average_stress_by_occupation, aes(x = reorder(Occupation, Average_Stress), y = Average_Stress, fill = Occupation)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  labs(title = "Average Stress Levels by Occupation",
       x = "Occupation",
       y = "Average Stress Level") +
  scale_fill_manual(values = rainbow(nrow(average_stress_by_occupation))) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```






---
```{r, echo=FALSE}
library(ggplot2)

ggplot(data = Sleep_dataset, aes(x = `Quality.of.Sleep`, y = `Sleep.Duration`)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Relacja pomiędzy jakością snu a długością snu",
       x = "Quality of Sleep",
       y = "Sleep Duration")


```






---
#Długość snu w zależności od wykonywanego zawodu

```{r, echo=FALSE}
ggplot(Sleep_dataset, aes(y = `Sleep.Duration`)) +
  geom_bar() +
  labs(x = "Count") +
  theme(axis.text.x=element_text(size=7, angle=90,hjust=0.99)) +
  facet_wrap(vars(Occupation))
```



---
```{r, echo=FALSE}
ggplot() + 
  geom_boxplot(data = Sleep_dataset, mapping = aes(y = `Daily.Steps`, x = Occupation)) +
  theme(axis.text.x=element_text(size=10, angle=45,hjust=0.95))
```




---
#Długość snu w zależności od aktywności fizycznej
- Ludzie, którzy dłużej śpią mają większy poziom aktywności fizycznej
```{r, echo=FALSE}
ggplot() + 
  geom_point(data = Sleep_dataset, mapping = aes(x = `Physical.Activity.Level`, y = `Sleep.Duration`)) +
  geom_smooth(data = Sleep_dataset, mapping = aes(x = `Physical.Activity.Level`, y = `Sleep.Duration`))
```




---
#Aktywność fizyczna i liczba kroków dziennych wykazywały silną korelację wynoszącą 0,77.

```{r, echo=FALSE}
set.seed(42)
#Here I create a correlation matrix with all the quantitative variables
cor(Sleep_dataset[c(3, 5, 6, 7, 8, 11, 12)])
```


```{r, echo=FALSE}
chisq_steps_physical <- chisq.test(table(Sleep_dataset$`Daily.Steps`,Sleep_dataset$`Physical.Activity.Level`))
chisq_steps_physical
```

```{r, echo=FALSE}
ggplot() + 
  geom_point(data = Sleep_dataset, mapping = aes(x = `Physical.Activity.Level`, y = `Daily.Steps`)) +
  geom_smooth(data = Sleep_dataset, mapping = aes(x = `Physical.Activity.Level`, y = `Daily.Steps`))
```



---
class: inverse, center, middle

# Section title

---

# Hello World

- Click the `Knit` button to compile your presentation

- Make sure to commit and push all resulting files to your GitHub repo

---

class: inverse, middle, center

# Using xaringan

---

# xaringan

- The presentation is created using the `xaringan` package

- Use `---` to separate slides and `--` for incremental builds

--
 
- Like this

---

# Layouts

You can use plain text

- or bullet points

.pull-left[
or text in two columns $^*$
]
.pull-right[
- like
- this
]

.footnote[
[*] And add footnotes
]

---

# Code```{r boring-regression}
# a boring regression
model <- lm(dist ~ speed, data = cars)
tidy(model)
glance(model)
```
---

#Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
iris_modified <- iris |>
  mutate(Species = fct_other(Species, keep = "setosa"))
```

```{r plot-iris, echo = FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = iris_modified, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species)) +
  geom_point() + 
  theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

---

## Plot and text

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
]

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

---

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

---

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# Feeling adventurous?

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer.

- And if you want more bells and whistles, there is also `xaringanExtra`: https://pkg.garrickadenbuie.com/xaringanExtra.
